---
title: "Recap from day 1"
output: html_document
---
```{r}
1. Shared/ cloud coding enviroment
2. Source control
3. Reproducible research via literate programming
4. R
  + package
  + functions
  + Data type
  + Object
  + Tidyverse paradigm
  + Logic construct
```

###Filter  exercises

1. Write a filter that gets all action movies from the movies dataset via the ggplot2movies package
2. Write a filter that removes films lasting more than 6 hours from the movies dataset
3. [ADVANCED] Write a filter that checks to see if any of the films don’t have any genres flagged at all

```{r}
library(tidyverse)
library(ggplot2movies)

## filter to all action movies

movies %>% 
  filter(Action == 1)

## Write a filter that removes films lasting more than 6 hours from the movies dataset

movies %>% 
  filter(length <= 6*60) %>% # 6  hours in minutes
  summarise(max(length)) # to check if it worked

# no genres

movies %>% 
  filter_at(vars(Action:Short), all_vars( . == 0)) ->
  movies_nogenre
```

###Using select

```{r}
iris %>% 
  select_if(is.numeric) %>% 
  prcomp()
```

##output movies with a named column

```{r}
movies %>% 
  rename(budget_if_known = budget) -> movies_cleaned

movies %>% 
  select(budget_if_known = budget, everything())
```
###Longer pipelines

```{r}
iris %>% 
  filter(Species=="Species") %>% ##put the reduction information in the right order
  select(starts_with("Sepal"))
```
###Amending columns (clean them up)
##mutate function allows us to change columns and create new columns
```{r}
iris %>% 
  mutate(Sepal.Length = Sepal.Length - 0.1,
Sepal.Area = Sepal.Length * Sepal.Width),
Species_trun= str_trunc(as,character(Species),3),
Diff.Sepal.Length=(Sepal.Length -
                     mean(Sepal.Length))/mean(Sepal.Length))

```
##Add a column to movies that says how much the length differs from the median

```{r}
movies %>% 
  mutate(diff_length=length - median(length)) ->
  movies_diff
  
```

##Aggregating our data
-groups = group_by
-aggregation =  summarise

```{r}
iris %>% 
  group_by(Species) %>% 
  summarise(count =  n(), avg.Sepal.Length = mean(Sepal.Length))

iris %>% 
  group_by(Species) %>% 
  summarise_all(mean)


```

###Exercises
1. Find the min and max values for length in movies
2. In a pipeline, find out what proportion of films are Action movies, Action Comedies, Comedies, and neither Action or Comedy

```{r}
movies %>%
  summarise(min(length)/60, max(length)/60)

movies %>% 
  group_by(Action, Comedy) %>% 
  summarise(n=n()) %>% 
  ungroup() %>% 
  mutate(per=n/sum(n)) %>% #chech step
  #summerise(sum(per))
  
```



